---
title: "growth of prisoners and convicts"
author: "Ridwan Setia Rahman"
date: "2/20/2022"
output:
  html_document: default
---

# Install dan Import Library

```{r}
# list_package = c('dplyr','forecast','echarts4r','readxl')
# install.packages(list_package)
library(dplyr)
library(forecast)
library(echarts4r)
library(readxl)
options(scipen = 100)
```

# DISCLAIMER

## The data used can be retrieved on the website

### <http://sdppublik.ditjenpas.go.id/analisis/public/grl/bulanan>

# import data on the number of occupants from 2012 to 2021

```{r}
hunian = read_excel("Dataset/JUMLAH HUNIAN.xlsx")
```

# Prisoner Data

## take data on the number of prisoner and make a line graph

```{r}
tahanan <- hunian[,2]
tahanan_ts = ts(tahanan,frequency = 12,start = c(2012,1))
plot(tahanan_ts)
```

## Prisoner data prediction with Forecasts Algorithm

### make predictions of prisoner data, calculate accuracy and enter into line graphs

```{r}
tah_mod = auto.arima(tahanan_ts)
tah_result = data.frame(tah_mod$fitted)
tahanan_predict = forecast(tah_mod,h = 6)
accuracy(tahanan_predict)
plot(tahanan_predict)
```

### make prediction data on the number of prisoners into a dataframe

```{r}
tahanan_predict = data.frame(tahanan_predict)
colnames(tahanan_predict)[colnames(tahanan_predict)=='Point.Forecast'] = 'Tahanan'
```

# Convict Data

## take data on the number of Convict and make a line graph

```{r}
napi <- hunian[,3]
napi_ts = ts(napi,frequency = 12,start = c(2012,1))
plot(napi_ts)
```

## Convict data prediction with Forecasts Algorithm

### make predictions of Convict data, calculate accuracy and enter into line graphs

```{r}
napi_mod = auto.arima(napi_ts)
napi_result = data.frame(napi_mod$fitted)
napi_predict = forecast(napi_mod,h = 6)
accuracy(napi_predict)
plot(napi_predict)
```

### make prediction data on the number of prisoners into a dataframe

```{r}
napi_predict = data.frame(napi_predict)
colnames(napi_predict)[colnames(napi_predict)=='Point.Forecast'] = 'Narapidana'
```

### Create Month Dataframe

```{r}
date.start.month=seq(as.Date("2022-01-01"),length=6,by="months")
df_b=data.frame(date.start.month)
bulan = df_b$date.start.month
```

## Merge Data

```{r}
data <- cbind(tahanan_predict,napi_predict)
data = round(data)
data = cbind(bulan,data)
prediksi <- data %>%
  select(bulan,Tahanan,Narapidana)%>%
  mutate(Jumlah = Tahanan+Narapidana)
names(prediksi) <- c('BULAN','TAHANAN','NAPI','JUMLAH HUNIAN')
hasil_data = rbind(hunian,prediksi)
names(hasil_data) <- c('Month','Prisoners','Convicts','Total')
hasil_data$Month <- format(hasil_data$Month, format ="%B %Y")
```

### Create interactive charts using echart

```{r}
hasil_data %>% 
  e_charts(Month) %>% 
  e_line(Prisoners, smooth = T) %>% 
  e_line(Convicts, smooth = T) %>% 
  e_line(Total, smooth = T)%>%
  e_axis_labels(x = "Year")%>%
  e_title("Number of prisoners and convicts", "2012-2021 and the predictions") %>% 
  e_legend(right=100)%>%
  e_theme("sakura")%>% 
  e_tooltip(trigger = "axis"
            #, formatter = e_tooltip_pointer_formatter("decimal")
            , axisPointer = list(
                type = "cross")
            , backgroundColor = "rgba(255,255,255,0.8)")
```
